On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-07-15 paper_lap/JCP_response1/05apparatus.tex
updating manuscript

For a panel $\gamma([s_1,s_2])$ with discretization nodes \upd{$x_i,\dots,x_{i+M-1}$} corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$). Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2.$ \upd{In~\cref{sec:appb}, we show that the interpolation error in the density
at panels away from the corner is related to the interpolation error in the solution to a related Dirichlet boundary value problem.}

>>>>

For a panel $\gamma([s_1,s_2])$ with discretization nodes \upd{$x_i,\dots,x_{i+M-1}$} corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$). Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2.$ \upd{In~\ref{sec:appb}, we show that the interpolation error in the density
at panels away from the corner is related to the interpolation error in the solution to a related Dirichlet boundary value problem.}

### 2020-07-15 paper_lap/JCP_response1/manuscript.tex
updating manuscript

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
\upd{
In this section, we demonstrate that for a panel which is sufficiently far from the corner, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [0,L]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary. Suppose that the boundary is discretized using the procedure discussed in~\cref{sec:resolve}. Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$, the corresponding weights are given by $w_{1}, \ldots w_{N}$, $X = \mathbb{L}^2({\Gamma})$, $\underline{X} = \mathbb{R}^{N}$, $\left< \cdot, \cdot \right>_{Y}$
denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$, and
$S:X \to \uX$ denote the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
\begin{equation}
S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots, f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, .
\end{equation}
Let $P:\underline{X} \to X$ denote the operator mapping the discretized samples to it's piecewise interpolant on the boundary.
Let $\Gamma_{\ell} = \gamma([s_{1},s_{2}])$ denote a panel that does not contain a corner vertex and is discretized with $M$ nodes  $x_{i},x_{i+1},\ldots x_{i+M-1}$.

@@

But first, we present a lemma about the accuracy of Gaussian quadrature
\begin{lemma}
\label{lem:b1}
Suppose that $p$ is a polynomial of degree less than $M$, then for any function $g$ in $\mathbb{L}^{2}[-1,1]$, then the integral
$\int_{-1}^{1} p \cdot g$ can be computed accurately using Gaussian quadrature of any order greater than or equal to $M$.
As a consequence, For any $g$ in $\mathbb{L}^{2}(\Gamma)$, then 
\begin{equation}
\left<h_{i},g \right>_{X} = \left< S[h_{i}], S[g] \right>_{\uX}
\end{equation}
\end{lemma}

>>>>

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
\upd{
In this section, we demonstrate that for a panel which is sufficiently far from the corner, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [0,L]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary. Suppose that the boundary is discretized using the procedure discussed in~\cref{sec:resolve}. Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$, the corresponding weights are given by $w_{1}, \ldots w_{N}$, $X = L^2({\Gamma})$, $\underline{X} = \mathbb{R}^{N}$, $\left< \cdot, \cdot \right>_{Y}$
denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$, and
$S:X \to \uX$ denote the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
\begin{equation}
S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots, f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, .
\end{equation}
Let $P:\underline{X} \to X$ denote the operator mapping the discretized samples to it's piecewise interpolant on the boundary.
Let $\Gamma_{\ell} = \gamma([s_{1},s_{2}])$ denote a panel that does not contain a corner vertex and is discretized with $M$ nodes  $x_{i},x_{i+1},\ldots x_{i+M-1}$.

@@

But first, we present a lemma about the accuracy of Gaussian quadrature
\begin{lemma}
\label{lem:b1}
Suppose that $p$ is a polynomial of degree less than $M$, then for any function $g$ in $L^{2}[-1,1]$, then the integral
$\int_{-1}^{1} p \cdot g$ can be computed accurately using Gaussian quadrature of any order greater than or equal to $M$.
As a consequence, For any $g$ in $\L^{2}(\Gamma)$, then 
\begin{equation}
\left<h_{i},g \right>_{X} = \left< S[h_{i}], S[g] \right>_{\uX}
\end{equation}
\end{lemma}
